---
title: "Using malariafit to fit malariasimple models with monty and hipercow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{working_with_monty}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dpi = 250,
  fig.width = 7
)
```

malariafit can also be used to help facilitate inference using monty and hipercow.

```{r, message = FALSE, results = "hide", fig.align = 'center', out.width='100%', fig.width = 6, fig.height = 4}
library(malariafit)
library(malariasimple)
library(dplyr)
params <- basic_parameters_site(example_site,
                                start_date = "2005-01-01",
                                end_date = "2010-12-31",
                                prevalence_rendering_min_ages = 0,
                                prevalence_rendering_max_ages = 5*365) |>
  set_interventions_site(example_site) |>
  set_seasonality_site(example_site) |> 
  malariasimple::set_equilibrium(init_EIR = 50)

output <- malariasimple::run_simulation(params) |> as.data.frame()
sim_data <- output[1:params$n_days %% 30 == 0,c("time","n_0_1825", "n_detect_0_1825")] #Assume monthly data
n_tests = 200 #Number of malaria tests given randomly each month
sim_data <- sim_data %>%
  mutate(tests = n_tests) %>%
  mutate(positive = rbinom(n=nrow(sim_data), size = n_tests, prob = n_detect_0_1825 / n_0_1825)) %>%
  dplyr::select(time, tests, positive)
plot(sim_data$time, sim_data$positive / sim_data$tests, type = "l", xlab = "Time", ylab = "Under 5 Prevalence")  
```

```{r, message = FALSE, results = "hide", fig.align = 'center', out.width='100%', fig.width = 6, fig.height = 4}
library(monty)
library(dust2)
gen <- malariasimple::malariasimple_deterministic()
filter <- dust2::dust_unfilter_create(gen, time_start = 0, data = sim_data, dt = 1/4)
packer <- monty::monty_packer(
  scalar = c("init_EIR"),
  process = function(x) {
    params <- basic_parameters_site(example_site,
                                    start_date = "2005-01-01",
                                    end_date = "2010-12-31",
                                    prevalence_rendering_min_age = 0,
                                    prevalence_rendering_max_age = 5*365) |>
      set_interventions_site(example_site) |>
      set_seasonality_site(example_site) |> 
      malariasimple::set_equilibrium(init_EIR = x$init_EIR)
  }
)
likelihood <- dust2::dust_likelihood_monty(filter, packer)
prior <- monty::monty_dsl({
  init_EIR ~ Uniform(10, 100)
})
vcv <- matrix(1)
sampler <- monty::monty_sampler_random_walk(vcv = vcv)
```

If we want to run large/many simulations, you may run out of core in a node. In which case it can be helpful to run chains across multiple nodes. These can be 'stitched' back together using `restitch_array()` to return it to a single array. We can then run some basic MCMC post-processing plots, or convert to formats for use with the `coda` or `bayesplot` packages. 

```{r, message = FALSE, results = "hide", fig.align = 'center', out.width='100%', fig.width = 6, fig.height = 4}
parameter_samples <- restitch_array(example_samples_list)
get_traceplot(parameter_samples)
get_dens_plot(parameter_samples, burn_in = 250)
```



